### 2020-06-04 manuscript/PLOS-MSc-Thesis.tex
general changes i don't remember

These two events conduce to the repression of the gene C by the gene A in the
rightmost part of the morphogenetic field and by the morphogen in the leftmost
part of the morphogenetic field, thus generating a lightly higher level of
expression of gene C in the center of the field. Because gene C activates its
own expression, a band of expression begins to form. This band of expression
then begins to activate the gene A also in the center of the field
(Fig~\ref{fig:topol9-dyn}).

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/topol-9-dynamics}
 \caption{\bf Dynamics of expression in topology number 9.}
 \label{fig:topol9-dyn}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%% copy of table environment %%%%%%%%%%%%%%%%%%%%%%%%
% \begin{table}[!ht]
% \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
% \centering
% \caption{{\bf Network descriptors of neutral network of topologies.}}
% \begin{tabular}{|l+l|l|l|l|l|l|l|}
% \hline
% \multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
% $cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
% $cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
% $cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
% \end{tabular}
% \begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
% \end{flushleft}
% \label{table1}
% \end{adjustwidth}
% \end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

It is interesting that the one-step neutral network

@@

This study can help us to understand the mechanisms by which the GRNs work in
nature as modules that make part of genomes, but it also can provide guidance
in the construction of new synthetic GRNs in the field of synthetic biology.

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 File.}
\label{S1_File}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Video.}
\label{S1_Video}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

>>>>

These two events conduce to the repression of the gene C by the gene A in the
rightmost part of the morphogenetic field and by the morphogen in the leftmost
part of the morphogenetic field, thus generating a lightly higher level of
expression of gene C in the center of the field. Because gene C activates its
own expression, a band of expression begins to form. This band of expression
then begins to activate the gene A also in the center of the field
(\nameref{S2_Fig}).
% (Fig~\ref{fig:topol9-dyn}).

% \begin{figure}[!h]
%  \includegraphics[width=\textwidth]{figures/results/topol-9-dynamics}
%  \caption{\bf Dynamics of expression in topology number 9.}
%  \label{fig:topol9-dyn}
% \end{figure}

@@

@@

The cladogram of spatiotemporal expression profiles shows that the genetic 
algorithm selected similar expression mechanisms that can be produced by very 
different topologies.

Although GRNs that produce a band of gene expression with only two nodes have 
been described (e.g. the I-zero motif, \cite{Schaerli2014}) this is to our 
knowledge the first time a GRN with a topology such as that of topology nine 
and its expression mechanism are reported, increasing our knowledge of the 
genotype-phenotype map in this kind of system.

However, it is still necessary to confirm experimentally the ability of this 
topology to generate the described pattern and it would be interesting to 
study its feasibility and possible implementation in synthetic gene regulatory 
networks.

@@

This study can help us to understand the mechanisms by which the GRNs work in
nature as modules that make part of genomes, and it also can provide guidance
in the construction of new synthetic GRNs in the field of synthetic biology.

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Relevant subgraphs present in the set of GRNs.}
%Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Dynamics of expression of topology number 9.}

% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Proportion of relevant subgraphs in the set of GRNs.}
